(Automatic) Speech Recognition Project --- Attacks on Neural Networks in a Lightweight Speech Pseudonymization Pipeline

### 2024-06-02 paper/paper.tex
Found correct code for setting targeted evasion attack

The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}

>>>>

The code used for the experiments performed can be found at the following URL: \url{https://github.com/daanbrugmans/ru-automatic-speech-recognition-23-24}.

\citet{kim2020torchattacks}
